---
title: "Parameterized Reporting Example"
params:
  dataloc: https://raw.githubusercontent.com/tidyverse/ggplot2/master/data-raw/mpg.csv
  dataname: mpg.csv
  manufacturer: pontiac
  date: !r lubridate::today()
output:
  html_document:
    df_print: paged
    theme: yeti
    toc: yes
    toc_depth: 3
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: hide
  pdf_document:
    toc: yes
    highlight: zenburn
  word_document:
    toc: yes
    highlight: zenburn
---


```{r setup, include = FALSE, message = FALSE, warning = FALSE}
# Knitr options: https://yihui.org/knitr/options/
library(lubridate)
library(dplyr)
library(plotly)
knitr::opts_chunk$set(collapse = TRUE
                      , eval = TRUE
                      , echo = TRUE
                      , message = FALSE
                      , warning = FALSE
                      , include = TRUE)
```


# About parametrized reports

This is a parameterized report written in in R Markdown. It consists of a combination of text and code chunks and uses `R`, `pandoc`, and `LaTeX` to connect to a data source, create visualizations, and export a single file to `html`, `pdf`, or `word` _without changing the code_. The resulting pages stand on their own, have no dependencies, and can be shared or stored on a central location, like git pages, a site on netlify, or a sharepoint documents library. The data and code are readily accessible for transparency and reproducibility.

Each export format has its own advantages:


|                         | html | word |  pdf  |
|-------------------------|:----:|:----:|:-----:|
|Standalone               | X    | X    | X     |
|Easy print               |      | X    | X     |
|Editable                 |      | X    |       |
|Static charts/maps       | X    | X    | X     |
|Interactive charts/maps  | X    |      |       |
|Embed data for download  | X    |      |       |

For good documentation, check out:  
* [Parameterized Reports (rmarkdown)](https://garrettgman.github.io/rmarkdown/developer_parameterized_reports.html)  
* [Knitting with parameters (bookdown)](https://bookdown.org/yihui/rmarkdown/params-knit.html#knit-with-custom-parameters)  
* [Parameterized R Markdown - incudes `marmap` example (rstudio)](https://docs.rstudio.com/connect/1.7.4/user/param-rmarkdown.html)  
* [Iterate multiple RMarkdown reports (rstudio community)](https://community.rstudio.com/t/iterate-multiple-rmarkdown-reports/43208)  


# Example Report for **`r params$manufacturer`** 

A couple different ways to pull down the file [(so reference)](https://stackoverflow.com/questions/14441729/read-a-csv-from-github-into-r)


```{r}
csv_url <- params$dataloc

download.file(csv_url, destfile = "mpg.csv", method = "curl")
df <- data.table::fread("mpg.csv")
```



## Parameter Specfic Charts {.tabset .tabset-fade .tabset-pills}

The manufacturer **`r params$manufacturer`** has **`r nrow(df[df$manufacturer == params$manufacturer, ])`** vehicles in this dataset.  
They average **`r mean(df[df$manufacturer == params$manufacturer, ]$cty)`** mpg city and **`r mean(df[df$manufacturer == params$manufacturer, ]$hwy)`** mpg highway. 

### Vehicle Counts

```{r}
df2 <- df[df$manufacturer == params$manufacturer, ]
  
plt <- ggplot(df2) +
  geom_bar( aes(x = as.factor(cyl), fill = as.factor(cyl)), stat = 'count') +
  scale_fill_viridis_d(option = "viridis") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none")

#ggplotly(plt)
plt
```

### MPGs

```{r}
df2 <- df[df$manufacturer == params$manufacturer, ]
  
plt <- ggplot(df2) +
  geom_point(aes(x = displ, y = hwy, color = as.factor(year), label = model), size = 5) +
  scale_color_viridis_d(option = "viridis") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none")

#ggplotly(plt)
plt
```



 
## All Car Manufacturers {.tabset .tabset-fade .tabset-pills}

### Vehicle Counts

```{r}
plt <- ggplot(df) +
  geom_bar( aes(manufacturer, fill = manufacturer), stat = 'count') +
  scale_fill_viridis_d(option = "viridis") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none")

#ggplotly(plt)
plt
```


### MPGs

```{r}
plt <- ggplot(df) +
  geom_point(aes(x = cty, y = hwy, color = manufacturer), alpha = 0.6) +
  scale_fill_viridis_d(option = "viridis") +
  facet_wrap(~manufacturer) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") 

#ggplotly(plt)
plt
```


<!-- This next snippet is executed manually (see chunk options) and not as part of render_report() -->

```{r, eval = FALSE, include = FALSE, echo = FALSE}
# Function to render this rmd file as an html doc; run this in R console
render_report = function(manufacturer = params$manufacturer, date = params$date) {
  rmarkdown::render(
    input = "parameterized-reporting-example.Rmd",
    output_format = "html_document",
    params = list(
      manufacturer = manufacturer,
      date = date
    ),
    output_file = paste0('reports/', manufacturer, "_mpg_report_", date, ".html")
  )
}

# Test one-off report with default params
render_report()

# Now loop through and create one report for each manufacturer
# (note: need to pull down the file and create `df` before running)
for (i in unique(df$manufacturer)){
  render_report(manufacturer = i)
  print(paste0('finished knitting ', i))
}
```
